Gelation as condensation frustrated by hydrodynamics and mechanical tension

### 2015-10-19 gel_cond/trunk/manuscript4.tex
Forgot g in the estimate of the Peclet number

To access roles of mechanics in the late stage, we realize the density matching of the order of 10$^{-4}$ and use a very accurate particle tracking method \cite{leocmach2013novel}. 

>>>>

To access roles of mechanics in the late stage, we realize a density matching of the order of 10$^{-4}$ (gravitational Peclet number $Pe< 10^{-6}$) and use a very accurate particle tracking method \cite{leocmach2013novel}. 
